--- 
title: "Annual Reports"
author: "Glen C. Falk"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Financial Aid Summary

## Cost of Attendance-Graduate
```{r echo=FALSE, COA-Grad-Resident}
c_pie_grad_res <- readRDS("c_pie_grad_res.rds")
c_pie_grad_res
```

```{r echo=FALSE, COA-Grad-Non_Resident, fig.cap='COA-Grad Non Resident',}
c_pie_grad_non <- readRDS("c_pie_grad_non.rds")
c_pie_grad_non
```

# ```{r fig-sub, fig.cap='two plots', fig.subcap=c('one plot', 'the other one'), out.width='33%', fig.asp=1, fig.ncol = 2}
# c_pie_grad_res
# c_pie_grad_non
# ```

```{r echo=FALSE, COA-Grad}
p_coa_gr <- readRDS("p_coa_gr.rds")
p_coa_gr
```


```{r echo=FALSE, Grad-COA}
coa_grad <- readRDS("coa_grad.rds")
coa_grad
```


This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
# install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

```{r tbl-summary, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
